---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tti

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/HopkinsIDD/tti.svg?branch=master)](https://travis-ci.org/HopkinsIDD/tti)
[![Codecov test coverage](https://codecov.io/gh/HopkinsIDD/tti/branch/master/graph/badge.svg)](https://codecov.io/gh/HopkinsIDD/tti?branch=master)
<!-- badges: end -->

The goal of tti is to facilitate the recursive calculation of infection proportions for the test-trace-isolate process.

## Installation

You can install the development version of tti from GitHub with:

``` r
devtools::install_github("HopkinsIDD/tti")
```

## Examples

```{r}
library(tti)
```

The `get_dqc_equilibrium()` function will iterate through the detected-quarantine-community vectors until "equilibrium" is met, as specified by the `tolerance` parameter. For example, here we start with 80% symptomatic in the community and 20% asymptomatic in the community.

```{r}
dqc <- get_dqc_equilibrium(init = c(Ds = 0, Da = 0, Qcds = 0, Qhds = 0,
                                    Qcda = 0, Qhda = 0, Qq = 0, Cs = 0.8,
                                    Ca = 0.2))
dqc
```

From this, we can calculate the proportion quarantined using the `get_prop_quarantined()` function.

```{r}
get_prop_quarantined(dqc)
```

We can then calculate the $R_{effective}$ under this scenario.

```{r}
get_r_effective(dqc)
```

The function `get_proportions_df()` will generate a data frame with four columns:  

* `t`: the time (iteration)  
* `prop_infected`: The proportion infected  
* `r_effective`: The effective R value
* `category`: The category

For example, to run the recursive function over 10 time points, we would run the following.

```{r}
d <- get_proportions_df(duration = 10)
d
```

```{r fig-example, message = FALSE, warning = FALSE}
library(ggplot2)
ggplot(d, aes(x = t, y = prop_infected, color = category)) + 
  geom_line() + 
  scale_y_continuous("Proportion of Infected")
```

We can then calculate the effective $R$ after each iteration.

```{r, message = FALSE, warning = FALSE}
library(dplyr)
r <- d %>%
  distinct(t, r_effective)
r
```

```{r eff-r}
ggplot(r, aes(x = t, y = r_effective)) +
  geom_line() +
  scale_y_continuous("Effective R")
```

We can also look at the $R_{effective}$ over a variety of parameters using the `get_r_effective_df()` function. This can take parameters as either single number scalars or vectors of parameters to try. For example, if we wanted to look at how $R$ is affected by varying `t_ds` between 1 and 14 and `rho_s` values of 0.05, 0.25, and 0.5, we would run the following.

```{r}
d <- get_r_effective_df(t_ds = 1:14, 
                        rho_s = c(0.05, 0.25, 0.5))
d
```

This gives us a data frame with 18 columns, the first being the $R_{effective}$ and the subsequent columns detailing the parameters. Notice here there are 52 rows, because we had 52 combinations of `t_ds` and `rho_s` that we provided.

```{r eff-r-sim}
ggplot(d, aes(x = t_ds, y = r_effective, color = factor(rho_s))) +
  geom_line() + 
  scale_y_continuous("Effective R") + 
  scale_x_continuous("Delay (symptomatic case detection and isolation)") + 
  scale_color_discrete("P(detected |  symptomatic)")
```

## Base functions

We also include some low-level functions that take any sized compartment vector along with a conformable infection matrix and detection matrix. These are meant for more experienced users familiar with the underlying mathematical model.

```{r}
infect <- matrix(c(2.5, 0, 0,
                   0, 1, 0,
                   0, 0, 2.5), nrow = 3, byrow = TRUE)
detect <- matrix(c(0.1, 0.5, 0.4,
                   0.02, 0.9, 0.08,
                   0.2, 0, 0.8), nrow = 3, byrow = TRUE)
dqc <- get_dqc_equilibrium_base(init = c(0, 0, 1), 
                                infect = infect,
                                detect = detect
                                )
dqc
```

```{r}
get_r_effective_base(dqc, infect)
```



