---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tti

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/HopkinsIDD/tti.svg?branch=master)](https://travis-ci.org/HopkinsIDD/tti)
[![Codecov test coverage](https://codecov.io/gh/HopkinsIDD/tti/branch/master/graph/badge.svg)](https://codecov.io/gh/HopkinsIDD/tti?branch=master)
<!-- badges: end -->

The goal of tti is to facilitate the recursive calculation of infection proportions for the test-trace-isolate process.

## Installation

You can install the development version of tti from GitHub with:

``` r
devtools::install_github("HopkinsIDD/tti")
```

## Example

```{r}
library(tti)
```

The `get_pqc_equilibrium()` function will iterate through the passive-quarantine-community vectors until "equilibrium" is met, as specified by the `tolerance` parameter. For example, here we start with 80% symptomatic in the community and 20% asymptomatic in the community.

```{r}
pqc <- get_pqc_equilibrium(init = c(Ps = 0, Pa = 0, Qcps = 0, Qhps = 0,
                             Qcpa = 0, Qhpa = 0, Qq = 0, Cs = 0.8,
                             Ca = 0.2))
pqc
```

From this, we can calculate the proportion quarantined using the `get_prop_quarantined()` function.

```{r}
get_prop_quarantined(pqc)
```

We can then calculate the $R_{effective}$ under this scenario.

```{r}
get_r_effective(pqc)
```

The function `get_proportions_df()` will generate a data frame with four columns:  

* `t`: the time (iteration)  
* `prop_infected`: The proportion infected  
* `r_effective`: The effective R value
* `category`: The category

For example, to run the recursive function over 10 time points, we would run the following.

```{r}
d <- get_proportions_df(duration = 10)
d
```

```{r fig-example, message = FALSE, warning = FALSE}
library(ggplot2)
ggplot(d, aes(x = t, y = prop_infected, color = category)) + 
  geom_line() + 
  scale_y_continuous("Proportion of Infected")
```

We can then calculate the effective $R$ after each iteration.

```{r, message = FALSE, warning = FALSE}
library(dplyr)
r <- d %>%
  distinct(t, r_effective)
r
```

```{r eff-r}
ggplot(r, aes(x = t, y = r_effective)) +
  geom_line() +
  scale_y_continuous("Effective R")
```

We can also look at the $R_{effective}$ over a variety of parameters using the `get_r_effective_df()` function. This can take parameters as either single number scalars or vectors of parameters to try. For example, if we wanted to look at how $R$ is affected by varying `t_ps` between 1 and 14 and `rho_s` values of 0.05, 0.25, and 0.5, we would run the following.

```{r}
d <- get_r_effective_df(t_ps = 1:14, 
                        rho_s = c(0.05, 0.25, 0.5))
d
```

This gives us a data frame with 18 columns, the first being the $R_{effective}$ and the subsequent columns detailing the parameters. Notice here there are 52 rows, because we had 52 combinations of `t_ps` and `rho_s` that we provided.

```{r eff-r-sim}
ggplot(d, aes(x = t_ps, y = r_effective, color = factor(rho_s))) +
  geom_line() + 
  scale_y_continuous("Effective R") + 
  scale_x_continuous("Delay (symptomatic passive detection)") + 
  scale_color_discrete("P(detected |  symptomatic)")
```


